{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Variational analysis, and Applications }

### 2025-01-10 Notebook LaTEX/Proposal/main.tex
>w<, changes

            One intriguingly detail in the Catalyst framework eluded us. 

@@

            From a complexity theoretical point of view, Catalyst acceleration didn't attempt at narrowing the lower complexity bound functions that are convex and nonsmooth and lack of any exact proximal oracle. 
            It is absolutely possible that, for any black box nonsmooth optimization problem, the same lower bound convergence rate $\mathcal O\left(1/\sqrt{k}\right)$ as stated in Theorem 3.2.1 in Nesterov's book \cite{nesterov_lectures_2018}. 
            Unfortunately it is absolutely nontrivial to see that is true because $\mathbb A$ optimizes Moreau Envelope $\mathcal M^*_{\kappa^{-1}F}(x)$ through inexact evaluation and the Moreau Envelope has Lipschitz gradient, for $\mathbb A$ Theorem 3.2.1 doesn't apply. 

>>>>

            One intriguing detail in the Catalyst framework eluded us. 

@@

            From a complexity theoretical point of view, Catalyst acceleration didn't attempt at narrowing the lower complexity bound bounds for functions that are convex and nonsmooth and lack of any exact proximal oracle. 
            It is absolutely possible that, for any black box nonsmooth optimization problem, the same lower bound convergence rate $\mathcal O\left(1/\sqrt{k}\right)$ as stated in Theorem 3.2.1 in Nesterov's book \cite{nesterov_lectures_2018} is true for Catalyst. 
            Unfortunately it is absolutely nontrivial to see that is true because $\mathbb A$ optimizes Moreau Envelope $\mathcal M^*_{\kappa^{-1}F}(x)$ through inexact evaluation and the Moreau Envelope has Lipschitz gradient. 
            For $\mathbb A$ Theorem 3.2.1 doesn't apply. 
